\def\DevnagVersion{2.17}% [[id:8e09a9a1-92fa-4da8-b006-0417cfaf6558][headers:1]]
\documentclass{tufte-book} 
\usepackage{devanagari}
\usepackage{amsmath}

\def\samaindent{\parindent=0.5in}
\def\dnitem#1{\noindent\llap{#1\space}\leftskip\parindent}

\begin{document}
\dnsamaveda
% headers:1 ends here

% [[id:b0d6e2a1-dd1f-4f73-a492-4ef4e7573c58][roopak:1]]
{\dn
\chapter{!pk}}
% roopak:1 ends here

% [[id:6cfaa744-7fbf-4ddd-835d-f0059b16fceb][Mohara:1]]
\subsection{ {\dn mohrA}}

{\dn \dnnum
{\dnsamaveda \samaindent
\dnitem{\rn{2}}

Etr\^{EkV}{\rn{1}}tktA Etr\^{EkV}{\rn{2}}DAEt.\\
DAEt\^{rEk}{\rn{3}}VDA Etr\^{EkV}{\rn{4}}DAEt.\\
DAEt\^{rEk}{\rn{5}}VDA Etr\^{EkV}{\rn{6}}DAEt.\\
\hspace{0.25in} \^{DA}{\rn{7}} \hspace{0.5in} \^{\35Fw}{\rn{8}} \hspace{0.25in}.\\
DAEt\^{rEk}{\rn{9}}VDA Etr\^{EkV}{\rn{10}}DAEt.\\
\hspace{0.25in} \^{DA}{\rn{11}} \hspace{0.5in} \^{\35Fw}{\rn{12}} \hspace{0.25in}.\\
DAEt\^{rEk}{\rn{13}}VDA Etr\^{Ekt}{\rn{14}}DAEt..\footnote{This is hard to get right if it is slowed down. Play it as
described, per matra.}
\\}}
{\dn \dnnum
{\dnsamaveda \samaindent
\dnitem{\rn{3}}

DAEtrEkVDA EtrEkVDAEt.

DAEtrEkVtk tAEtrEkVtk.

DAEtrEkVtk tAEtrEkVtk.\footnote{Plain repetition}

EtrEkVtktA EtrEkVDAEt DA.

EtrEkVtktA EtrEkVDAEt DA.

EtrEkVtktA EtrEkVDAEt..\footnote{Last repetition of tihai does not have the final dha!}

}}
% Mohara:1 ends here

% [[id:8ebf9727-ce5b-426b-9684-48f0c0a529b6][Kamali chakradhar paran:1]]
\subsection{ {\dn kmAlF c\387wDAr prn {\rs (\re}aAdA cArtAl !pk{\rs )\re}}}


{\dn \dnnum
{\dnsamaveda %\samaindent
\dnitem{\rn{1}}\footnote{28-11-09}

\9{k}DA\9{k} DAk\381w . DAEtrEkVtk DA . DAEtrEkVtk DA .

DAEtrEkVtk tAEtrEkVtk . ED\2ED\2 EtVEtV . \9{k}DAEtV kE\381wV .

DAEtrEkVDA EtEVkt . DA DA . DA \35Fw . \9{k}DAEtV kE\381wV .

DAEtrEkVDA EtEVkt . DA DA . DA \35Fw . \9{k}DAEtV kE\381wV .

DAEtrEkVDA EtVkt . DA DA . DA \35Fw ..  {\NormalFont $\times$} \rn{3}

}}
% Kamali chakradhar paran:1 ends here

% [[id:8d6b8c82-88af-4fc1-8a93-fc59cf604bc0][ektaal:1]]
{\dn\chapter{ ek tAl}}
% ektaal:1 ends here

% [[id:6a3e3597-31bd-426b-82cb-838f725da20c][kaayda:1]]
\subsection{{\dn kAydA \dnnum \rn{1}}}

{\dn \dnnum
{\dnsamaveda \samaindent
\dnitem{kAydA}

EDVDAG\? nADAEtrEkV EDVDA\35Fw EDVDG\? .\\
nADAEtrEkV EtnAG\?nA EtVtAG\? nAtAEtrEkV .\\
EtVtA\35FwEDVDAG\? nADAEtrEkV EDnAG\?nA .

\dnitem{plVA \rn{1}}

EDVDAG\? nADAEtrEkV EDVDAG\? nADAEtrEkV .\\
EDVDAG\? nADAEtrEkV EDVDAG\? nADAEtrEkV .\\
EDVDA\35Fw EDVDAG\? nADAEtrEkV EtnAG\?nA .\\
EtVtAG\? nAtAEtrEkV EtVtAG\? nAtAEtrEkV .\\
EtVtAG\? nAtAEtrEkV EDVDAG\? nAtAEtrEkV .\\
EDVDA\35Fw EDVDAG\? nADAEtrEkV EtnAG\?nA ..

\dnitem{\rn{1}{\rs -\re}\rn{2}}

EDVDAG\?  EDVDAG\? EDVEDV EDVDAG\? .\\
EDVDAG\? nADAEtrEkV EDVDAG\? nADAEtrEkV .\\
EDVDA\35Fw EDVDAG\? nADAEtrEkV EtnAG\?nA .\\
EtVDAk\?  EtVtAk\? EtVEtV EtVtAk\? .\\
EtVtAG\? nAtAEtrEkV EDVDAG\? nAtAEtrEkV .\\
EDVDA\35Fw EDVDAG\? nADAEtrEkV EtnAG\?nA ..

\dnitem{\rn{1}{\rs -\re}\rn{3}}

EDVDAG\?  nAEDEVDA G\?nAEDEV EDEVDAG\?.\\
nADAG\?nA  EtnAG\?nA EDVDAG\? nADAEtrEkV.\\
EDVDA\35Fw EDVDAG\? nADAEtrEkV EtnAG\?nA .\\
EtVtk\?  nAEtVtA k\?nAEtEV EtEV tk\?.\\
nAtAk\?nA  EtnAG\?nA EDVDAG\? nADAEtrEkV.\\
EDVDA\35Fw EDVDAG\? nADAEtrEkV EtnAG\?nA ..

\dnitem{\rn{1}{\rs -\re}\rn{4}}

EDVDAG\?  EtnAG\?nA EDVDAG\? EtnAG\?nA .\\
EDVDAG\? nADAEtrEkV  EDVDAG\? nADAEtrEkV.\\
EDVDA\35Fw EDVDAG\? nADAEtrEkV EtnAG\?nA .\\
EtVtAk\?  EtnAk\?nA EtVtAk\? EtnAk\?nA .\\
EtVtAk\? nAtAEtrEkV  EDVDAG\? nADAEtrEkV.\\
EDVDA\35Fw EDVDAG\? nADAEtrEkV EtnAG\?nA ..

\dnitem{EthA{}I}

EDVDAG\? nADAEtrEkV EDVDAG\? EDnAG\?nA .\\
DAEDnA G\?nADA EDnAG\?nA DA\35Fw .\\
\35FwEDV DAG\?nADA EtrEkVEDV DAG\?EDnA .\\
G\?nADA EDnAG\?nA DAEDnA G\?nADA.\\
\35Fw\35Fw EDVG\? nADAEtrEkV EDVDAg\4 .\\
EDnAG\?nA DAEDnA G\?nADA EDnAG\?n ..

}}
% kaayda:1 ends here

% [[id:9e751d45-0887-4086-aa4e-c1bbf810eb3c][teen taal:1]]
{\dn\chapter{ tFn tAl}}
% teen taal:1 ends here

% [[id:c7ef4519-4c61-4e66-8b2b-6e61fc1bd479][Japtaal:1]]
{\dn\chapter{ JptAl}}
% Japtaal:1 ends here

% [[id:1d4cc68a-d527-45fa-8d48-a660300c5b90][Peshkara:1]]
\subsection{{\dn p\?fkArA}}
\noindent
{\dn 

DF?X ED\2tA . DADA ED\2tA ED\2nA .

\35FwktA DADA . ED\2tA ED\2nA \35FwkDA .

tF?X Et\2tA . tAtA Et\2tA Et\2nA .

\35FwktA DADA . ED\2t ED\2nA \35FwkDA ..
}
% Peshkara:1 ends here

% [[id:135d85e8-d773-4216-8a40-66fcec6f9fbc][Tilvada:1]]
{\dn
\chapter{EtlvAXA}}
\subsection{{\dn T\?kA}}
\noindent
{\dn

DA EtrEkV ED\2 t\qq{t} . ED\2DA DADAG\? Et\2 Et\2 .

tA EtrEkV ED\2 t\qq{t} . ED\2DA DADAG\? ED\2 ED\2 ..
}
% Tilvada:1 ends here

% [[id:e9dc86e4-a234-452f-a773-d32b0b385969][footer:1]]
\vfill
\begin{center}
\texttt{--Exported automatically from org-mode on \today--}
\end{center}
\end{document}
% footer:1 ends here
